---
title: "Solutions for Homework I"
author: "Uğurcan Bayraktar"
date: "11/15/2021"
output:
  pdf_document: default
  html_document: default
---
### Question 1

Firstly, we import the tidyverse.

```{r, message=FALSE}
library(tidyverse)
options(dplyr.print_max = 1e9)
options(scipen = 100)
```

Then, the data should be read. It is assigned to **revenue_data.**


```{r, message=FALSE}
revenue_data <- read_csv("data/Revenue_Chart_Full_Data_data.csv")
```

### Question 2

*Year (copy)*, *Format*, *Value (Actual)* columns are renamed below.  
  

```{r}
revenue_annually = revenue_data %>%
                    select(`Year (copy)`, Format, `Value (Actual)`) %>%
                    rename(Year = `Year (copy)`,
                           Format = Format,
                           Value = `Value (Actual)`)
```

This is the first 6 rows of the subset.

```{r, echo=FALSE}
knitr::kable(head(revenue_annually))
```

Then the year column is sorted.

```{r}
revenue_annually = revenue_annually %>%
                  filter(Year >= 2018) %>%
                  arrange(Year)
```

```{r, echo=FALSE}
knitr::kable(head(revenue_annually))
```


  
Finally, annually revenue is calculated  from 2018 to 2020.
  
```{r}
revenue_annually = revenue_annually %>%
                    group_by(Year) %>%
                    summarise(`Value (Yearly)` = sum(Value))
```

```{r, echo=FALSE}
knitr::kable(revenue_annually)
```


### Question 3

Created a subset that includes the streaming formats.

```{r}
streaming_revenue = revenue_data %>%
                      select(Year, Streaming = Format, Value = `Value (Actual)`) %>%
                      filter(Streaming %in% c("Paid Subscription",
                                           "On-Demand Streaming (Ad-Supported)",
                                           "Other Ad-Supported Streaming",
                                           "SoundExchange Distributions",
                                           "Limited Tier Paid Subscription"),
                                            Year == 2020) %>%
                      arrange(Streaming)
```

```{r, echo=FALSE}
knitr::kable(head(streaming_revenue))
```


The total streaming music revenue is approximately $10.1 billion in 2020.

```{r}
streaming_revenue = streaming_revenue %>%
                      group_by(Year)%>%
                      summarise(`Streaming Revenue` = sum(Value))
```

```{r, echo=FALSE}
knitr::kable(streaming_revenue)
```

### Question 4

To begin with, I created a subset named as **revenue_share**, then made a new column which is named as **Categories** consists of _Streaming_, _Synchronization_, _Physical_, _Digital Downloads_ and _Other_ categories. 

```{r}
revenue_share = revenue_data %>%
                  select(Year, Format, Value= `Value (Actual)`) %>%
                  filter(Year == 2020) %>%
                  mutate(Category = case_when(
                    Format %in% c("Paid Subscription",
                                  "On-Demand Streaming (Ad-Supported)",
                                  "Other Ad-Supported Streaming",
                                  "SoundExchange Distributions",
                                  "Limited Tier Paid Subscription") ~ "Streaming",
                    Format %in% c("Synchronization") ~ "Synchronization",
                    Format %in% c("LP/EP", "CD") ~ "Physical",
                    Format %in% c("Download Album",
                                  "Download Single") ~ "Digital Downloads",
                    TRUE ~ "Other"))
```

Finally, I created a new column includes a revenue shares as percentages and sorted in decreasing order.

```{r}
revenue_share = revenue_share %>%
                  group_by(Category) %>%
                  summarise(Revenue_Total = sum(Value)) %>%
                  mutate(Share = round(Revenue_Total / sum(Revenue_Total),2)) %>%
                  arrange(-Share)
```

```{r, echo = FALSE}
knitr::kable(revenue_share)
```

### Question 5

Radio revenue data is created below. It includes _SoundExchange Distributions_ and _Other Ad-Supported Streaming_ revenues from 2018 to 2020.

```{r}
radio_revenue <- revenue_data %>%
                    select(Year, Format, Value = `Value (For Charting)`) %>%
                    filter(Year >= 2018,
                           Format %in% c("SoundExchange Distributions",
                                         "Other Ad-Supported Streaming")) %>%
                    arrange(Year)
```

Here is another subset created for charting the **annually revenues** in the **radio revenue** data.

```{r}
radrev_annually <- radio_revenue %>%
                    group_by(Year) %>%
                    summarise(Value_Annually = sum(Value))
```

Graph is created below.

```{r}
#Creating graph with ggplot
#Filled the stack bars in order with levels
g <- ggplot(radio_revenue, aes(x = Year,
                               y = Value,
                               fill = factor(Format,
                                             levels = c("Other Ad-Supported Streaming",
                                                        "SoundExchange Distributions")))) +
       geom_bar(stat = "identity") + #Bar graph will be used
       
       #Labels are created as same as the original figure.
       labs(x = "", y = "$ MILLIONS",
            title = "U.S. DIGITAL AND CUSTOMIZED RADIO REVENUES",
            subtitle = "Source: RIAA")+
  
       #Theme is updated: title, subtitle and legend are adjusted.
       theme(plot.title = element_text(size = 14, face = "bold", hjust = 0.5),
            plot.subtitle = element_text(hjust = 0.5),
            legend.position = c(0.5,0),
            legend.margin = margin(0,0,-23,0),
            legend.box.margin = margin(0,0,-23,0),
            legend.direction = "horizontal",
            legend.text = element_text(size = 11)) +
            #Filling colors: Online hex identifier is used to obtain hex values.
            scale_fill_manual("", 
                       values = c("SoundExchange Distributions"  = "#2d7a7a",
                                  "Other Ad-Supported Streaming" = "#c2da74"))
```

Combined our graph with the annual revenues.

```{r}
g + 
  #Background and axes are removed. 
  #Text of x axis and the title of y axis are resized and positioned properly.
  theme(panel.background = element_blank(),
          axis.ticks = element_blank(),
          axis.line = element_blank(),
          axis.text.y  = element_blank(),
          axis.text.x = element_text(vjust = 5, size = 12),
          axis.title.y = element_text(size = 12)) +
  #X axis  was not at the bottom of the stacked bar,
  #Therefore geom_hline() is used to create an x axis same as the original figure.
  geom_hline(yintercept = 0) +

  #Text for the value of annual revenue is created. Adjusted its text, font and position properly.
  geom_text(aes(Year, Value_Annually, 
                label = sprintf("$%d", round(Value_Annually)), fontface=2, fill = NULL),
                size = 4.25, vjust = -0.25, data = radrev_annually)
```
