---
title: "Solutions for Homework I"
author: "Uğurcan Bayraktar"
date: "11/2/2021"
output:
  pdf_document: default
  word_document: default
  html_document: default
---

Firstly, we import the tidyverse.

```{r, message=FALSE}
library(tidyverse)
options(dplyr.print_max = 1e9)
options(scipen = 100)
```

Then, the data should be read. It is assigned to **revenue_data.**

```{r, message=FALSE}
revenue_data <- read_csv("data/Revenue_Chart_Full_Data_data.csv")
```

### Question 1

*Year (copy)*, *Format*, *Value (Actual)* columns are renamed below.  
  

```{r}
revenue_annually = revenue_data %>%
                    select(`Year (copy)`, Format, `Value (Actual)`) %>%
                    rename(Year = `Year (copy)`,
                           Format = Format,
                           Value = `Value (Actual)`)
```

This is the first 6 rows of the subset.

```{r, echo=FALSE}
knitr::kable(head(revenue_annually))
```

Then the year column is sorted.

```{r}
revenue_annually = revenue_annually %>%
                  filter(Year >= 2018) %>%
                  arrange(Year)
```

```{r, echo=FALSE}
knitr::kable(head(revenue_annually))
```


  
Finally, calculated annually revenue from 2018 to 2020.
  
```{r}
revenue_annually = revenue_annually %>%
                    group_by(Year) %>%
                    summarise(`Value (Yearly)` = sum(Value))
```

```{r, echo=FALSE}
knitr::kable(revenue_annually)
```


### Question 2

Created a subset which is including the streaming formats.

```{r}
streaming_revenue = revenue_data %>%
                      select(Year, Streaming = Format, Value = `Value (Actual)`) %>%
                      filter(Streaming %in% c("Paid Subscription",
                                           "On-Demand Streaming (Ad-Supported)",
                                           "Other Ad-Supported Streaming",
                                           "SoundExchange Distributions",
                                           "Limited Tier Paid Subscription"),
                                            Year == 2020) %>%
                      arrange(Streaming)
```

```{r, echo=FALSE}
knitr::kable(head(streaming_revenue))
```


The total streaming music revenue is approximately $10.1 billion in 2020.

```{r}
streaming_revenue = streaming_revenue %>%
                      group_by(Year)%>%
                      summarise(`Streaming Revenue` = sum(Value))
```

```{r, echo=FALSE}
knitr::kable(streaming_revenue)
```

### Question 3

To begin with, I created a subset named as **revenue_share**, then made a new column which is named as **Categories** consists of _Streaming_, _Synchronization_, _Physical_, _Digital Downloads_ and _Other_ categories. 

```{r}
revenue_share = revenue_data %>%
                  select(Year, Format, Value= `Value (Actual)`) %>%
                  filter(Year == 2020) %>%
                  mutate(Category = case_when(
                    Format %in% c("Paid Subscription",
                                  "On-Demand Streaming (Ad-Supported)",
                                  "Other Ad-Supported Streaming",
                                  "SoundExchange Distributions",
                                  "Limited Tier Paid Subscription") ~ "Streaming",
                    Format %in% c("Synchronization") ~ "Synchronization",
                    Format %in% c("LP/EP", "CD") ~ "Physical",
                    Format %in% c("Download Album",
                                  "Download Single") ~ "Digital Downloads",
                    TRUE ~ "Other"))
```

Finally, I created a new column includes a revenue shares as percentages and sorted in decreasing order.

```{r}
revenue_share = revenue_share %>%
                  group_by(Category) %>%
                  summarise(Revenue_Total = sum(Value)) %>%
                  mutate(Share = round(Revenue_Total / sum(Revenue_Total),2)) %>%
                  arrange(-Share)
```

```{r, echo = FALSE}
knitr::kable(revenue_share)
```





















